%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer - Audio Algorithms} % Job title
    {Netflix} % Organization
    {Seattle, WA} % Location
    {Nov. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Algorithm design for audio content analysis \& understanding. Research, prototyping \& product-ization}
        \item {Training \& maintaining Audio ML models for scaled Post-production \& Globalization tasks}
        \item {Construction of large-scale audio-video training datasets}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Staff Engineer} % Job title
    {Marchex} % Organization
    {Seattle, WA} % Location
    {Sept. 2014 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Algorithm design, prototyping, implementation, performance analysis \& optimization}
        \item {Develop audio-dsp algorithms for language \& telephony SPAM identification}
        \item {Construct corpora for conversational speech recognition. Design automatic data selection algorithms}
        \item {Train, deploy \& maintain custom DNN-HMM models in Kaldi. Experiment with novel end-to-end ASR architectures}
        \item {Perform 24/7 on-call support of fleet processing 1M calls/day. Extensive experience with AWS EC2 \{LB, ASG, EFS, EBS\}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Audio Applications Engineer} % Job title
    {Dolby Laboratories} % Organization
    {San Francisco, CA} % Location
    {Jan. 2012 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on embedded systems implementations/ports of Dolby's perceptual audio coding \& audio post-processing}
        \item {Algorithms: MDCT, spectral extension, hybrid complex QMF, dialog, bass \& volume leveling, surround virtualization}
		\item {Extensive experience conducting acoustic measurements \& critical listening}
        \item {Mentored junior engineers \& regularly lectured on Dolby's audio-dsp algorithms to APAC FAE staff}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Audio Software Engineer} % Job title
    {Apple} % Organization
    {Cupertino, CA} % Location
    {Feb. 2006 - Nov. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{2006 - 2009}: Developed system level audio \& effect processing features for Soundtrack Pro v2, Final Cut Studio 2 \& 3} 
        \item {Integrated, fixed bugs and maintained audio-unit hosting code for Logic Pro audio effects within ST Pro, Final Cut Pro X}
        \item {\textbf{2010-2011}: Developed \& shipped an audio auto-synch tool \& a multi-channel audio file configuration classifier for FCP X}        
		\item {Collaborated with the CoreAudio team on optimizations to their resampler \& audio analysis algorithms}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Software Engineer} % Job title
    {2KSports} % Organization
    {San Rafael, CA} % Location
    {May 2005 - Jan. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed C/C++ tools \& libraries for the XBOX360 launch of NBA2k6, NHL2k6, College Hoops 2K6}
        \item {Performed support tasks to game development teams using the audio library}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
	